Title Goes Here

### 2025-04-17 analysis/supplementary-materials/appendix1.qmd
SOM SEM color codes added

# Prepare the energy ranges
energy_ranges <- list(
  C = c(0.2, 0.3),
  O = c(0.5, 0.6),
  F = c(0.67, 0.69),
  Na = c(1.04, 1.06),
  Mg = c(1.25, 1.27),
  Mg_beta = c(1.3, 1.4),
  Al = c(1.48, 1.5),
  Si = c(1.7, 1.8),
  P = c(2, 2.1),
  S = c(2.3, 2.32),
  S_beta = c(2.46, 2.47),
  Cl = c(2.62, 2.64),
  K = c(3.31, 3.33),
  K_beta = c(3.59, 3.61),
  Ca = c(3.68, 3.7),
  Ca_beta = c(4.01, 4.02),
  Ca_L = c(0.34, 0.36),
  Ti = c(4.5, 4.6),
  Ti_beta = c(4.9, 5),
  Ti_L = c(0.45, 0.47),
  Fe = c(6.38, 6.41),
  Fe_beta = c(7, 7.2),
  Fe_L = c(0.69, 0.73))

>>>>

# Prepare the energy ranges
energy_ranges <- list(
  C = c(0.2, 0.3), # "#584B9F" dark blue
  O = c(0.5, 0.6), # "#0086B3" blue
  F = c(0.67, 0.69), # "#3EADA9"  greenish blue
  Na = c(1.04, 1.06), # "#4FC46A"  green"
  Mg = c(1.25, 1.27), # "#AEC491" yellowish green
  Mg_b = c(1.3, 1.4), # "#AEC491" yellowish green
  Al = c(1.48, 1.5), # "#F2C86C" yellow
  Si = c(1.7, 1.8), # "#F5A838" orange
  P = c(2, 2.1), # "#EE850E" dark orange
  S = c(2.3, 2.32), # "#D54F34" red
  S_b = c(2.46, 2.47), # "#D54F34" red
  Cl = c(2.62, 2.64), # "#A51122" wine
  K = c(3.31, 3.33), # "#A71B4B" pinkish red
  K_b = c(3.59, 3.61), # "#A71B4B" pinkish red
  Ca = c(3.68, 3.7), # "#D35C79" pink
  Ca_b = c(4.01, 4.02), # "#D35C79" pink
  Ca_L = c(0.34, 0.36), # "#D35C79" pink
  Ti = c(4.5, 4.6), # "#BD3977" light purple
  Ti_b = c(4.9, 5), # "#BD3977" light purple
  Ti_L = c(0.45, 0.47), # "#BD3977" light purple
  Fe = c(6.38, 6.41), # "#762181" purple
  Fe_b = c(7, 7.2), # "#762181" purple
  Fe_L = c(0.69, 0.73)) # "#762181" purple
